%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	\vspace{-1mm}

%---------------------------------------------------------
  \cventry
    {Master's Graduate Research} % Job title
    {Oklahoma State University} % Organization
    {Stillwater, OK} % Location
    {Aug. 2016 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Investigated conformation sampling of tetravalent molecules and ice water structures}
        \item{Simplified ice water structure generation}
        \item{Created highly parallelized programs to guide a semi-random walk to optimize molecule structure.}
        \item{Concluded in verbal defense and Master's Thesis}
		\vspace{-2mm}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Undergraduate Independent Research} % Job title
{Southern Nazarene University} % Organization
{Bethany, OK} % Location
{Aug. 2015 - May 2016} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Led investigation into adsorption properties of graphene on alkenes and alkynes.}
		\item{Synthesized and tested properties of graphene with magnetite.}
		\item{Designed and built a workstation for basic computational research for the department.}
		\vspace{-2mm}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Field Biology Semester Abroad, San Gerardo de Dota} % Job title
{Southern Nazarene University} % Organization
{Costa Rica} % Location
{Jan. - May 2014} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Identified and measured hundreds of trees in a primary growth plot.}
		\item{Plotted measurements with collaborative data to measure the effects of climate change on the region.}
		\item{Presented findings in Spanish to local community}
		\vspace{-2.5mm}
	\end{cvitems}
}

%---------------------------------------------------------
%\cventry
%{Independent Research} % Job title
%{Independent} % Organization
%{Olathe, KS} % Location
%{June - July 2016} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item{Replicated publication on an approach to synthesize graphene using household materials.}
%		\item{Continued work and further collaborated with Southern Nazarene University.}
%	\end{cvitems}
%}

%---------------------------------------------------------


\end{cventries}
