%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Technical Analyst} % Job title
{Paycom Payroll} % Organization
{Oklahoma City, OK} % Location
{July 2019 - Current} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{External client-facing support for time-management hardware. \textbf{rework}}
		\item{Internal client-facing support assisting 3000+ employee transition to work-from-home environment.}
		\item{Redesigned multiple key processes related to asset management, including significant code work.}
		\item{Created several novel solutions to improve support quality and reduce hardware replacement rate.}
		\item{Support quality metrics rate in top 3 of all employees in this position. \textbf{rework}}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Automation Consultant} % Job title
{Self-Employed} % Organization
{Oklahoma City, OK} % Location
{Jan. 2019 - Apr. 2020} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Independent contractor providing automation solutions for repetitive and time-intensive workflow tasks.}
		\item{Involved creation and maintenance of software tools that interface with programs to unify the user experience.}
		\item{Recent contract involved improving company workflow by 10\% through automation tools.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Computer Systems Contractor} % Job title
{Self-Employed} % Organization
{Oklahoma City, OK} % Location
{June 2013 - Apr. 2020} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{As-needed computer specialist providing on-site tech support and customized hardware solutions.}
		\item{Prioritized hardware purchases to provide a cost-effective solution and excellent end-user experience.}
	\end{cvitems}
}

%%---------------------------------------------------------
%\cventry
%{Creative Intern} % Job title
%{Nazarene Publishing House} % Organization
%{Lenexa, KS} % Location
%{Summers 2012-2014} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item{Assisted with various Adobe Creative Suite projects}
%		\item{Explored public relations applications of 3D printers at conferences.}
%		\item{Assisted with raw footage ingest into archive.}
%	\end{cvitems}
%}

%---------------------------------------------------------
\cventry
{Technology Intern} % Job title
{Southern Nazarene University} % Organization
{Bethany, OK} % Location
{Jan. - Dec. 2013} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Directly worked with the Vice President of Information Technology.}
		\item{Assisted in preparation of smart devices for Board of Trustees meetings.}
		\item{Led investigations into possible technologies of interest to the university staff and students.}
	\end{cvitems}
}

%---------------------------------------------------------
%\cventry
%{Technology Intern} % Job title
%{Premier Studios} % Organization
%{Lenexa, KS} % Location
%{Summers 2007-2012} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Assisted with multiple global Nazarene General Assemblies as a workshop technology troubleshooting expert.}
%		\item{Assisted with archive tape duplication and management.}
%		\item{Single-handedly organized and boxed over 15,000 backup tapes.}
%	\end{cvitems}
%}

%---------------------------------------------------------



\end{cventries}
